% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Why I'm Bad and How To Improve\\ Part 1 (of many)}

% Please do not change the subtitle
\subtitle{COMP150 - CPD Report}

% Please put your student number in the author field
\author{1600689}

\begin{document}

\maketitle

\section{Introduction}

Overall my career goals are quite broad as I have known from a young age that I want to work in and contribute to the gaming industry as it has been a big part of my life. I chose to start conceptualising games and learning to program them to help to gain the skills required to work in the gaming industry. One skill that that I have noticed that I’m terrible at is \textit{version control on GitHub}, another skill I need to improve on is \textit{academic writing}, a third skill that needs improving is \textit{time management}, a fourth skill that needs improving is effectively \textit{presenting my ideas in a pitch} to make it so that others fully understand my ideas, a fifth skill that needs to be improved would be applying \textit{PEP-8 guidelines} to the code that I am writing.

\section{Version Control - GitHub}

Over this semester I have majorly struggled to use version control purely due to the fact that I keep forgetting to upload my work to GitHub on a regular bases, this is mainly due to the fact that this is the first time I have had to integrate version control into my work, meaning that I’m not used to having to upload my work at regular intervals and while this has not had much effect on the work currently, I can see how not using version control can be detrimental to the work I would be contributing to a team. This did become more apparent during the creation of the convicted prototype as we were all contributing to different parts of the code and we needed to make sure that each different part of the code still worked in conjunction with each other or, can be rolled back to a previous version. To get better at this I will actively try to use GitHub more when going over the new content to complete for next semester as this will help me to get into the habit of frequently uploading my work to GitHub as I do it not when I complete it.

\section{Academic Writing - Essays}

Throughout my assignments this semester I have found that I have struggled slightly with writing academically as it is much different to how I have been taught to write, this is probably quite evident in the way I have written all my essays and assignments so far. I can see how this could very quickly become problematic as it means that my writing will not be very professional and might not get the points across that it needs to making what I write far less effective, this could lead to people not reading all my work or taking it much less seriously. This could potentially render my work useless and a waste of time and money. To improve I will look in more depth how to write more efficiently and professionally over the next couple of months through different sources such as books, the internet, and different academic papers as this will help me increase the overall quality of my written communication and how effective my writing is when writing papers.

\section{Time Management - Removing Myself From Busy Environments}

Overall throughout my time this semester I have found that I am not the best when it comes to efficiently managing my time to make sure that I am not rushing around to submit work before the deadline. This could be very detrimental in the future as it can lead to high stress, lack of sleep, sloppy work, and the possibility to miss the deadline. For me personally I think that removing myself from busy environments such as the games studio and my flat would be highly beneficial as it would give me a quieter environment to work in allowing me to focus more on my work. I also think this would be a good thing to do with my teams as it would allow for more concentrated work to be done allowing for high efficiency. To do this, when we get back from the Christmas break I will now hold quite a lot of my meetings in quieter more remote locations where people are less likely to be distracted such as the library, I will also start to do more of my work in the silent study space of the library to make sure that I am working efficiently, without distractions.

\section{Presenting Ideas in a Pitch}

Another skill I also need to work on is presenting pitches as I have found that I become quite shaky and nervous before and during my pitches. This is bad as there are many different and important reasons why I would need to pitch my ideas to others in the industry such as an investment pitch. If I can’t clearly and concisely, with confidence, present my ideas in a marketable way then I won’t be taken seriously and no one will want to invest in my potential projects. This would halt my progression through the gaming industry as no one would be investing any time or money into my games. I feel that a good way to improve on this would be to practice pitches of new ideas and to put myself into new situations where I must improvise to an audience as this would help when doing pitches if any questions are asked about any ideas or concepts. I will try and do this over the next two months by getting my team to listen to different pitches and critically analyse and give constructive criticism on my performance.

\section{Complying With PEP-8}

A fifth skill that I wasn’t too good at was following PEP-8 guidelines while writing code as it is difficult to try and write with the guidelines while trying to get different projects to function. This could be bad for the maintainability of the code as PEP-8 makes the code much easier to read and understand meaning that if PEP-8 isn’t used while writing code, if it is given to others to modify or update, it might be impossible to edit as there might not be proper formatting or no notes to explain what the code is doing in different sections. To improve on this I will go over the PEP-8 guidelines to make sure that any existing and any new code is written to the guidelines. This is important within the gaming industry as if code isn’t formatted in any way when working in large groups on big projects none of the code will work together making each person’s contribution meaningless and would not produce a viable product. This could also very heavily prolong the progress of a project if different bits of code aren’t being written properly first time around.

\section{Conclusion}

To conclude, over the next 2-3 months I will use GitHub more to efficiently use version control, I will learn more about academic writing so that my written communication can be improved in my work, I will work in more confined places to work more efficiently, I will work on my confidence and my public speaking to help me pitch my ideas and I will learn to use formatting to improve the maintainability of my code. These things will help me towards gaining my career goals by allowing me to progress through the gaming industry by more effectively through improving my skills to effectively create and share my ideas with other people.

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
